---
params: 
    title: ""
    Pars: "`r list()`"
    plotPars: "`r list()`"
    tabs: "`r TRUE`"
    its: " `r numeric()`"
    nyears: " `r numeric()`"
    proyears: " `r numeric()`"
    date: "`r Sys.Date()`"
title: "`r params$title`"
date: "`r params$date`"
output:
  html_document
---


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Growth Parameters {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Growth Parameters')
}

dd <- params$Pars$M_ageArray %>% dim()
nsim <- dd[1]
maxage <- dd[2]

nsamp <- length(params$its)
```

#### Sampled Parameters 
Histograms of `r nsim` simulations of von Bertalanffy growth parameters `Linf`, `K`, and `t0`, and inter-annual variability in Linf and K (`Linfsd` and `Ksd`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
MSEtool:::plot.Growth(params$Pars, nsamp=nsamp, plotPars=params$plotPars, plot.num=1)
```

#### Time-Series
The Linf and K parameters in each year for `r nsamp` simulations. The vertical dashed line indicates the end of the historical period:

```{r, echo=FALSE}
MSEtool:::plot.Growth(params$Pars, nsamp=nsamp, plotPars=params$plotPars, plot.num=2)
```

#### Growth Curves
Sampled length-at-age curves for `r nsamp` simulations in the first historical year, the last historical year, and the last projection year.

```{r, echo=FALSE}
MSEtool:::plot.Growth(params$Pars, nsamp=nsamp, plotPars=params$plotPars, plot.num=3)
```

