---
params: 
    title: ""
    Pars: "`r list()`"
    plotPars: "`r list()`"
    tabs: "`r TRUE`"
    its: " `r numeric()`"
    nyears: " `r numeric()`"
    proyears: " `r numeric()`"
    date: "`r Sys.Date()`"
title: "`r params$title`"
date: "`r params$date`"
output:
  html_document
---


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Maturity Parameters {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Maturity Parameters')
}

dd <- params$Pars$M_ageArray %>% dim()
nsim <- dd[1]
maxage <- dd[2]

nsamp <- length(params$its)
```

#### Sampled Parameters 
Histograms of `r nsim` simulations of `L50` (length at 50% maturity), and `L95` (length at 95% maturity), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
MSEtool:::plot.Maturity(params$Pars, nsamp=nsamp, plotPars=params$plotPars, plot.num=1)

```

#### Maturity at Age and Length 
Maturity-at-age and -length for `r nsamp` simulations in the first historical year, the last historical year (i.e., current year), 
and the last projected year:

```{r, echo=FALSE}
MSEtool:::plot.Maturity(params$Pars, nsamp=nsamp, plotPars=params$plotPars, plot.num=2)
```


