---
params: 
    title: ""
    Pars: "`r list()`"
    plotPars: "`r list()`"
    tabs: "`r TRUE`"
    its: " `r numeric()`"
    nyears: " `r numeric()`"
    proyears: " `r numeric()`"
    date: "`r Sys.Date()`"
title: "`r params$title`"
date: "`r params$date`"
output:
  html_document
---


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Maturity Parameters {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Maturity Parameters')
}

dd <- params$Pars$M_ageArray %>% dim()
nsim <- dd[1]
maxage <- dd[2]

nsamp <- length(params$its)
```

#### Sampled Parameters 
Histograms of `r nsim` simulations of `L50` (length at 50% maturity), `L95` (length at 95% maturity), and corresponding derived age at maturity parameters (`A50` and `A95`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
par(mfrow=c(2,2))
hist2(Pars$Stock$L50, col=params$plotPars$col, axes=params$plotPars$axes, main="L50", breaks=params$plotPars$breaks)
abline(v=Pars$Stock$L50[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1)

hist2(Pars$Stock$L95, col=params$plotPars$col, axes=params$plotPars$axes, main="L95", breaks=params$plotPars$breaks)
abline(v=Pars$Stock$L95[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1)

hist2(Pars$Stock$ageM, col=params$plotPars$col, axes=params$plotPars$axes, main="A50", breaks=params$plotPars$breaks)
abline(v=Pars$Stock$ageM[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1)

hist2(Pars$Stock$age95, col=params$plotPars$col, axes=params$plotPars$axes, main="A95", breaks=params$plotPars$breaks)
abline(v=Pars$Stock$age95[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1)

```

#### Maturity at Age and Length 
Maturity-at-age and -length for `r nsamp` simulations in the first historical year, the last historical year (i.e., current year), 
and the last projected year:

```{r, echo=FALSE}
par(mfrow=c(1,2))
slope <- log(19)/(Pars$Stock$L95-Pars$Stock$L50)
Ls <- seq(0, to=max(Pars$Stock$Linf), length.out=200)
maxage <- Pars$Stock$maxage

Mat_len <- sapply(params$its, function(X)  plogis(Ls, Pars$Stock$L50[X], 1/slope[X]))
matplot(Ls, Mat_len, type="l", bty="l", main="Maturity-at-length", lwd=params$plotPars$lwd, lty=1, 
        ylab="Probability", xlab="Length", ylim=c(0,1), xpd=NA)

matplot(0:maxage, t(Pars$Stock$Mat_age[params$its,,nyears]), type="l", bty="l", main="Maturity-at-age", lwd=params$plotPars$lwd, 
        lty=1, axes=FALSE, xlim=c(0, max(Pars$Stock$maxage)), ylab="", xlab="Age", ylim=c(0,1), xpd=NA)
axis(side=1)
axis(side=2, labels=FALSE)

```


