---
params: 
    title: ""
    Pars: "`r list()`"
    plotPars: "`r list()`"
    tabs: "`r TRUE`"
    its: " `r numeric()`"
    nyears: " `r numeric()`"
    proyears: " `r numeric()`"
    date: "`r Sys.Date()`"
title: "`r params$title`"
date: "`r params$date`"
output:
  html_document:
    toc: true
    toc_float: true
---

## Observation Parameters
```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Catch Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Catch Observations')
}
Pars <- params$Pars
nsim <- Pars$Obs$Csd %>% length()
```


#### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in catch observations (`Csd`) and persistent bias in observed catch (`Cbias`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
par(mfrow=c(1,2))
hist2(Pars$Obs$Csd, main="Csd", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Csd[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$Cbias, main="Cbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Cbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

```

#### Time-Series
Time-series plots of catch observation error for historical and projection years:

```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(1,1,1,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(Pars$Obs$Cobs_y[params$its, ]))
matplot(years, t(Pars$Obs$Cobs_y[params$its, ]),
        type="l", lty=1, bty="l", main="Catch discrepancy by Year", 
        lwd=params$plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Depletion Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Depletion Observations')
}
```

#### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in depletion observations (`Dobs`) and persistent bias in observed depletion (`Dbias`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:


```{r, echo=FALSE}
par(mfrow=c(1,2))
hist2(Pars$Obs$Derr, main="Dobs", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Derr[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$Dbias, main="Dbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Dbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 



```

#### Time-Series
Time-series plots of depletion observation error for historical and projection years:

```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(1,1,1,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(Pars$Obs$Derr_y))
matplot(years, t(Pars$Obs$Derr_y[params$its, ]),
        type="l", lty=1, bty="l", main="Depletion discrepancy by Year", 
        lwd=params$plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```




```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Abundance Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Abundance Observations')
}
```

#### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in abundance observations (`Btobs`) and persistent bias in observed abundance (`Btbias`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
par(mfrow=c(1,2))
hist2(Pars$Obs$Aerr, main="Btobs", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Aerr[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$Abias, main="Btbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Abias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

```

#### Time-Series
Time-series plots of abundance observation error for historical and projection years:

```{r, echo=FALSE}

par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(1,1,1,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(Pars$Obs$Aerr_y[params$its,]))
matplot(years, t(Pars$Obs$Aerr_y[params$its, ]),
        type="l", lty=1, bty="l", main="Abundance discrepancy by Year", 
        lwd=params$plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```




```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Index Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Index Observations')
}
```

#### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in index observations (`Iobs`) and hyper-stability/depletion in observed index (`beta`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
if (!is.null(Pars$Obs$betas)) {
  par(mfrow=c(1,2))  
}

if (!is.null(Pars$Obs$I_beta)) {
  par(mfrow=c(1,4))  
}

hist2(Pars$Obs$Isd, main="Iobs", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Isd[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

if (!is.null(Pars$Obs$betas)) {
  hist2(Pars$Obs$betas, main="beta", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$betas[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 
}

if (!is.null(Pars$Obs$I_beta)) {
  hist2(Pars$Obs$I_beta, main="I_beta", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
  abline(v=Pars$Obs$I_beta[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
  axis(side=1) 
  
  hist2(Pars$Obs$SpI_beta, main="SpI_beta", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
  abline(v=Pars$Obs$SpI_beta[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
  axis(side=1) 
  
  hist2(Pars$Obs$VI_beta, main="VI_beta", col=params$plotPars$col, axes=params$plotPars$axes,
     breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
  abline(v=Pars$Obs$VI_beta[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
  axis(side=1) 
}


```

#### Time-Series
Time-series plot of `r nsamp` samples of index observation error:

```{r, echo=FALSE}

par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(4,1,3,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(Pars$Obs$Ierr_y[params$its, ]))
matplot(years, t(Pars$Obs$Ierr_y[params$its, ]),
        type="l", lty=1, bty="l", main="Index observation error by Year", 
        lwd=params$plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```

Plot showing an example true abundance index (blue) with `r nsamp` samples of index observation error and the hyper-stability/depletion parameter (`beta`):

```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(4,1,3,1))
ind<-seq(1,0.1,length.out=nyears)


if (!is.null(Pars$Obs$betas)) {
  beta <- Pars$Obs$betas[params$its]
}

if (!is.null(Pars$Obs$I_beta)) {
  beta <- Pars$Obs$I_beta[params$its]
}

Imu<-array(rep(ind,each=nsamp)^rep(beta,nyears),
           c(nsamp,nyears))*Pars$Obs$Ierr_y[params$its, 1:nyears]
Imu<-Imu/apply(Imu,1,mean)
ind <- ind/mean(ind)

ylim <- range(c(ind,Imu))
plot(1:nyears, ind, type="l", ylim=ylim, bty="l", las=1, xlab="Years", 
     ylab="Relative Abundance", lwd=2, col="blue", xpd=NA,
     main="Observed Index with beta parameter")
matplot(t(Imu), add=TRUE, type="l", lwd=params$plotPars$lwd)
legend("topright", bty="n", col=c("blue", 1:nsamp), lwd=params$plotPars$lwd, 
       legend=c("True Index", paste0("Observed", 1:nsamp, sep=" ")), lty=c(1, 1:nsamp))
```


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Recruitment Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Recruitment Observations')
}
```

#### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in index observations (`Recsd`) , with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}

par(mfrow=c(1,1))
hist2(Pars$Obs$Recsd, main="Recsd", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Recsd[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 
```

<!-- # to add hbiascv -->

#### Time-Series
Timeseries plots of observeration error for recruitment:

```{r, echo=FALSE}

par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(1,1,1,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(Pars$Obs$Recerr_y[params$its, ]))
matplot(years, t(Pars$Obs$Recerr_y[params$its, ]),
        type="l", lty=1, bty="l", main="Recruitment index discrepancy by Year", 
        lwd=params$plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```



```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Composition Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Composition Observations')
}
```

#### Sampled Parameters
Histograms of `r nsim` simulations of catch-at-age effective sample size (`CAA_ESS`) and sample size (`CAA_nsamp`) and catch-at-length effective (`CAL_ESS`) and actual sample size (`CAL_nsamp`) with vertical colored lines indicating `r nsamp` randomly drawn values:

```{r, echo=FALSE}
par(mfrow=c(2,2))
hist2(Pars$Obs$CAA_ESS, main="CAA_ESS", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$CAA_ESS[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$CAA_nsamp, main="CAA_nsamp", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$CAA_nsamp[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1)

hist2(Pars$Obs$CAL_ESS, main="CAL_ESS", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$CAL_ESS[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$CAL_nsamp, main="CAL_nsamp", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$CAL_nsamp[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1)
```


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Parameter Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Parameter Observations')
}
```

#### Sampled Parameters
Histograms of `r nsim` simulations of bias in observed natural mortality (`Mbias`), von Bertalanffy growth function parameters (`Linfbias`, `Kbias`, and `t0bias`), length-at-maturity (`lenMbias`), and bias in observed length at first capture (`LFCbias`) and first length at full capture (`LFSbias`) with vertical colored lines indicating `r nsamp` randomly drawn values:

```{r, echo=FALSE}
par(mfrow=c(2,2))
hist2(Pars$Obs$Mbias, main="Mbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Mbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1)

hist2(Pars$Obs$Linfbias, main="Linfbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Linfbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$Kbias, main="Kbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Kbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$t0bias, main="t0bias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$t0bias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

par(mfrow=c(1,3))
hist2(Pars$Obs$lenMbias, main="lenMbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$lenMbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$LFCbias, main="LFCbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$LFCbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$LFSbias, main="LFSbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$LFSbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

```



```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('### Reference Point Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('### Reference Point Observations')
}
```

#### Sampled Parameters
Histograms of `r nsim` simulations of bias in observed FMSY/M (`FMSY_Mbias`), BMSY/B0 (`BMSY_B0bias`), reference index (`Irefbias`), reference abundance (`Brefbias`) and reference catch (`Crefbias`), with vertical colored lines indicating `r nsamp` randomly drawn values:


```{r, echo=FALSE}
par(mfrow=c(2,3))
hist2(Pars$Obs$FMSY_Mbias, main="FMSY_Mbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$FMSY_Mbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1)

hist2(Pars$Obs$BMSY_B0bias, main="BMSY_B0bias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$BMSY_B0bias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$Irefbias, main="Irefbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Irefbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Obs$Brefbias, main="Brefbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Brefbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 


hist2(Pars$Obs$Crefbias, main="Crefbias", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Obs$Crefbias[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 


```


